\documentclass[a4paper]{article}
% \usepackage[margin=1.25in]{geometry}
\usepackage[inner=2.0cm,outer=2.0cm,top=2.5cm,bottom=2.5cm]{geometry}
% \usepackage{ctex}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{braket}

\newcommand{\homework}[5]{
    \pagestyle{myheadings}
    \thispagestyle{plain}
    \newpage
    \setcounter{page}{1}
    \noindent
    \begin{center}
    \framebox{
        \vbox{\vspace{2mm}
        \hbox to 6.28in { {\bf Optimization Methods \hfill #2} }
        \vspace{6mm}
        \hbox to 6.28in { {\Large \hfill #1 \hfill} }
        \vspace{6mm}
        \hbox to 6.28in { {\it Instructor: {\rm #3} \hfill Name: {\rm #4}, StudentId: {\rm #5}}}
        \vspace{2mm}}
    }
    \end{center}
    % \markboth{#4 -- #1}{#4 -- #1}
    \vspace*{4mm}
}


\newenvironment{solution}
{\color{blue} \paragraph{Solution.}}
{\newline \qed}

\begin{document}
%- Write your name and id here
\homework{Homework 2}{Fall 2021}{Lijun Zhang}{Student name}{Student id}

\paragraph{Notice}
\begin{itemize}
    \item The submission email is: \textbf{zhangzhenyao@lamda.nju.edu.cn}.
    \item Please use the provided \LaTeX{} file as a template.
    \item If you are not familiar with \LaTeX{}, you can also use Word to generate a \textbf{PDF} file.
\end{itemize}

\paragraph{Problem 1: Convex functions}
~\\

\begin{enumerate}[a)]
	\item Prove  that the function~$f : \mathbb{R}^n_{++} \rightarrow \mathbb{R}$, defined as
    \begin{equation}
    f(x) = - \sum^n_{i=1} \log (x_i), \notag
    \end{equation}
    is strictly convex.

	\item Let~$f$~be twice differentiable, with~$dom(f)$~convex. Prove that~$f$~is convex if and only if
    \begin{equation}
    \left( \nabla f(x) - \nabla f(y) \right)^T (x - y) \geqslant 0, \notag
    \end{equation}
    for all x, y.

    \item Let~$f : \mathbb{R}^n \rightarrow \mathbb{R}$~be a function. Its perspective transform~$g : \mathbb{R}^{n+1} \rightarrow \mathbb{R}$~is defined by
    \begin{equation}
    g(x, t) = t f(\frac{x}{t}), \notag
    \end{equation}
    with domain~$dom(g) = \{(x, t) \in \mathbb{R}^{n+1} : x \in dom(f), t > 0\}$. Use the definition of convexity to prove that if~$f$~is convex, then so is its perspective transform~$g$.
\end{enumerate}


% \begin{solution}
% Write your answer here.
% \end{solution}


\paragraph{Problem 2: Concave function}
~\\

\noindent
Suppose~$p < 1, p \neq 0$. Show that the function
\begin{equation}
f(x) = \left( \sum^n_{i=1} x^p_i \right)^{\frac{1}{p}} \notag
\end{equation}
with~$dom(f) = \mathbb{R}_{++}$~is concave.


% \begin{solution}
% Write your answer here.
% \end{solution}


\paragraph{Problem 3: Convexity}
~\\

\noindent
Let~$\psi : \Omega \mapsto \mathbb{R}$~be a strictly convex and continuously differentiable function. We define
\begin{equation}
\Delta_{\psi} (x, y) = \psi(x) - \psi(y) - \Braket{\nabla \psi(y), x - y}, ~~\forall x, y \in \Omega. \notag
\end{equation}

\begin{enumerate}[a)]
    \item Prove that~$\psi(x, y) \geqslant 0$, $\forall x, y \in \Omega$~and the equality holds only when~$x = y$.
    
    \item Let~$L$~be a convex and differentiable function defined on~$\Omega$~and~$C \subset \Omega$~be a convex set. 
    Let~$x_0 \in \Omega - C$ and define
    \begin{equation}
        x^* = \mathop{\arg\min}\limits_{x \in C} L(x) + \Delta_{\psi} (x, x_0). \notag
    \end{equation}
    Prove that for any~$y \in C$,
    \begin{equation}
        L(y) + \Delta_{\psi}(y, x_0) \geqslant L(x^*) + \Delta_{\psi} (x^*, x_0) + \Delta_{\psi} (y, x^*). \notag
    \end{equation}
\end{enumerate}

% \begin{solution}
% Write your answer here.
% \end{solution}

\paragraph{Problem 4: Projection}
~\\

\noindent
For any point~$y$, the projection onto a nonempty and closed convex set~$X$~is defined as
\begin{equation}
\Pi_X (y) = \mathop{\arg\min}\limits_{x \in X} \frac{1}{2} \Vert x - y \Vert^2_2. \notag
\end{equation}

\begin{enumerate}[a)]
    \item Prove that~$\Vert \Pi_X (x) - \Pi_X (y) \Vert^2_2 \leqslant \Braket{\Pi_X (x) - \Pi_X (y), x - y}$.

    \item Prove that~$\Vert \Pi_X (x) - \Pi_X (y) \Vert_2 \leqslant \Vert x - y \Vert_2$.
\end{enumerate}


% \begin{solution}
% Write your answer here.
% \end{solution}

\paragraph{Problem 5: Conjugate Function}
~\\

\noindent
Derive the conjugates of the following functions.
\begin{enumerate}[a)]
    \item $f(x) = \max \{0, 1 - x\}$.

    \item $f(x) = \ln (1 + e^{-x})$.
\end{enumerate}


% \begin{solution}
% Write your answer here.
% \end{solution}

\end{document}
